\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}


\begin{document}
% Needs work %
\begin{enumerate}
\item
Timmy walks out of his house and starts repeatedly turning left. Under what conditions does he return to his starting location?

\item
Timmy walks out of his house and down the road. He starts repeatedly taking the first left. Given that he can always take another left prove that he must return to his initial position

\item
A particle is thrown from point A at angle $\theta$ from the ground with initial velocity $u$ metres per second. At the same instant the ball is thrown a pole with base $B$ $d$ metres from $A$ and with length $L$ is knocked so as to give it a angular velocity $\omega$. Given that the particle collides with the end of the pole. What is $\omega$ in terms of $u$, $L$, $d$ and $\theta$?

\item
In the board game risk player 1 launches a attack from a territory with $x$ units against a territory with $y$ units. Assuming player 1 doesn’t give up their assault. For what $x$ and $y$ can we expect player 1 to capture the territory?

\item
A particle like chicken is launched horizontally from a height $h$ with initial velocity $v$. The chicken bounces in such a way such that it’s vertical velocity after bouncing is $ur$ where $u$ is the velocity before bouncing and $r$ is a constant such that $0 < r < 1$. How far does the chicken travel horizontally?

% Easy Q1-3%
\item
There are three jars. One with red fruit, one with blue fruit and one with red and blue fruit. You can’t see inside the jars. Ammar has mischievously relabelled the jars, but foolishly he tells you that each label is on the wrong jar. Provide a strategy such that you can correctly relabel the jars by checking a random fruit from a jar of your choice

\item
Standing in line perfect logician puzzle

% Relatively easy %
\item
Square in circle with identical angles problem

\item
A particle is launched from a height h at a angle of Theta, with an initial velocity of u. Given that it lands at Pi/4 degrees to the horizontal, what was its initial Theta.

% Hard Geometry %
\item
A empty cone with height H and radius R is filled with water such that the
 Rate of change of volume filled with respect to time is F. Find the rate of change of the surface area of the water with respect to time. The cone is now tilted so as to be at a angle of Theta. What is the rate of change of the surface area of the water with respect to time?

\item
You are driving in a circle with constant speed. There are two windmills in the circle PROVIDE NESSASARY VARIABLES. What is the first time at which the 4 of the windturbine sporks apear to be edges of a 4-gon.

\item
A number n is x more than a multiple of y and v more than a multiple of w. Show that there is no n. Deduce that it is not the n that bends but you

\item
Prove that for all integer n. 14n+13 and 21n+20 are coprime

\item
A satellite is in orbit around a planet. The satellite drops a ball down to the planet. The ball bounces off the planet in such a way that maintains it’s kinetic energy and flips it’s direction. Given that the ball returns to the satellite having had the satellite completed a orbit. ...?

\item
Show that any two elements (both greater than one) drawn from the same row of Pascal's triangle have greatest common divisor greater than one.  For example, the greatest common divisor of 28 and 70 is 14

% Medium Popular result Geometry Q4-8 %
\item
Find all A, B, C and D such that for all n, hcf(An + C, Bn + D) = 1

\item
Prove that for all prime p. (p-1)! + 1 is divisible by p.

% Hard (I don't think people would get my solution but there may be a simplier one) %
\item
A function $f(x)$ is defined as follows. $f''(x) = -f(x)$, $f(0) = 0$ and $f'(0) = 1$. Prove that:
\begin{enumerate}
    \item $f(x + a) = f(x)f'(a) + f'(x)f(a)$
    \item $(f(x))^2 + (f'(x))^2 = 1$
    \item $\exists x$ $f(x+a) = f'(x)$
\end{enumerate}
You may use without proof that fact that any linear second order differential equation with initial conditions has a unique solution

% Easy Probability (if the question is clear) %
\item
George is running a D\&D session but his only dice is a d20. Describe a strategy so as to handle all required rolls fairly

% Relatively easy %
\item
You are given a normal die and a blank die.

How can you label the blank die using the numbers 0 to 6 so that when you roll the two dice the sum shows each whole number from 1 to 12 with equal chance

\item
Something about matrix ERO

\item
Orbit problem I still haven't finished

\item
Potential derivation of optics formula

% Nice result. Perceived difficulty will vary %
\item
Proof that certain games have a forced win

\item
Particle on dome velocity question

% Relatively Hard Evaluating Integral (Calculus) %
\item
Evaluate
$\int_{0}^{\pi}(\frac{xsin(x)}{3 + sin^2(x)})dx$

\item
Dice ranges game

% Hard Probability %
\item
Kathrine rolls $k$ d6. Norman rolls $n$ d6. $n > k$. What is the probability that the sum of the numbers on Kathrine's dice is greater than the sum of the number on Norman's dice?

% Medium Graphing %
\item
Sketch $sin(x+a)sin(x+b)$

% Relatively easy Nice result (difficulty will vary) %
\item
Prove that any operation when repeatedly applied to a Rubik's cube will eventually return it to it's initial position

% Relatively easy (difficulty will vary) %
\item
Prove that there exists no operation that when applied to the Rubik's cube will cycle through all possible moves

\item
When playing on a eliptical pool table a ball hit from one foci will always enter the hole in the other focus. The rules for bouncing are energy concervation and the angle of incidence are equal to the angle of reflection.

\item
Five children (Ammar, Bilal, Chris, Dan and Egan) raced each other.  First they raced to the spreading chestnut tree, and then they raced back to their starting point. The following facts are known:
\begin{enumerate}
	\item Ammar was fourth in the race to the tree.
	\item The person who was last to the tree managed to win the race back.
	\item The person who won the race to the tree was third on the way back.
	\item The person who was third in the race to the tree was second on the way back.
	\item Bilal was fourth on the way back.
	\item Chris reached the tree before Dan.
	\item Chris got back to the start before Egan.
\end{enumerate}
For  each  race  (to  the  tree  and  back  again),  write  down  the  order  in  which  the  children finished.

\item
Sphere packing problem

% Very hard %
\item
Show that for any 2n+1 natural numbers n can always be picked such that the sum of the n selected terms is divisable by n

\item
Timmy the gnome was wondering home. He takes a path up a hill that follows the curve y = e^x. Given that he starts at a gradient of 0.0025 and ends at a gradient of 8. What length is his path up the hill?

\item
Walking round house

\item
Evaluate
\int_{0}^{\frac{\pi}{2}} \frac{\sin^3{x}}{2 + \sin(x)} dx

\item
For what \theta such that 0 \leq \theta \geq 2\pi is \sin(x) + \cos(x) \geq 0

\end{enumerate}
\end{document}
