% Medium Elementary problem Q2-6 %
\item
I have two identical but non-uniform ropes. I know that if I light one end of either rope it will burn for exactly one hour. How can I time 45 minutes? (I have a lighter of some sort).

% Would like to rephrase question. I am yet to actually prove this. I take the result currently on good faith %
\item
When playing on a eliptical pool table a ball hit from one foci will always enter the hole in the other focus. The rules for bouncing are energy concervation and the angle of incidence are equal to the angle of reflection.

% Relatively easy Q1-5 %
\item
The minute and hour hands on a analog clock overlap at 12 o’clock. Where else do they overlap?

% I think it makes for a nice question. Though upon further consideration it is not as difficult as I had thought %
\item
A function $f(x)$ is defined as follows. $f''(x) = -f(x)$, $f(0) = 0$ and $f'(0) = 1$. Prove that:
\begin{enumerate}
    \item $f(x + a) = f(x)f'(a) + f'(x)f(a)$
    \item $(f(x))^2 + (f'(x))^2 = 1$
    \item $\exists x$ $f(x+a) = f'(x)$
\end{enumerate}
You may use without proof that fact that any linear second order differential equation with initial conditions has a unique solution

% I am aware that most have not proven the converse of Pythagorus. In either case it's a useful result %
\item
A triangle $T$ has sides $a$, $b$ and $c$ where $c$ is the longest length.

Prove that: T is right angled \iff $a^2 + b^2 = c^2$

\item
Timmy the gnome lives at the end of exponential road. Exponential road is a road up a mountain that matches a segment of the graph y = e^x. Exponential road starts at a gradient of 0.0025 and ends with gradient 8. One day Timmy the gnome was wondering home, starting at the beginning of exponential road how long is the path Timmy takes to travel home

% Easy Q1 %
\item
5 points ate placed in a 1x1 square. Show that no matter where the points are placed there will always be a pair of points with a distance of less than or equal to $\frac{1}{\sqrt{2}}$ between them

% I'm trying to do a weekly diffrential equation question. Would gladly accept a diffrent diffrential equation problem %
\item
Newton's law of cooling states that the rate of heat transfer of a body is directly proportional to the difference in the temperature between the body and its surroundings. This leads the objects to tend towards the same temperature. A can of coke with 
temperature 15 degrees is placed in a fridge kept at constant tempereature of 5 degrees. Given that it takes 2 minutes for the can of coke to reach 10 degrees how long does it take to reach a temperature of 7.5 degrees? (Do some reaserch into coke cooling times)

% Medium Probability Q6-10 (I note that people seem to struggle with probability questions, perhaps relatively hard) %
\item
Siddarth and Dan are playing a Tennis match. For each point there is a probability of $p$ that Siddarth wins. What is the probability that Siddarth wins the set?
